---
title: "Online Learning Platform"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(DT)
library(data.table)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(wordcloud2)
library(tidytext)

assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")

opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}

source("../Reports/functions.R")
source("../Reports/constants.R")

```

```{r constants}

```

```{r read_data}

#data for skills required
dat_dice <- fread(input = "../Data/dice_com-job_us_sample.csv", verbose = F)
dat_2 <- fread(input = "../Data/career_builder.csv", verbose = F)

#data for course analyses
dat <- fread(input = "../Data/Udemy_Course_info.csv", verbose = F)

#data for sentiment analyses
udemy.comments <- fread(input ="../Data/Udemy_Comments.csv")

```

```{r prep_data skills}

#dat_dice
# Step 1: Create a vector of all skills
all_skills_2 <- unlist(strsplit(dat_dice$skills, ", "))

# Step 2: Calculate frequency of each skill
skill_counts_2 <- tibble(skill = all_skills_2) %>%
  count(skill, sort = TRUE)

#dat_2
# Step 1: Create a vector of all skills
all_skills <- unlist(strsplit(dat_2$skills, ", "))

# Step 2: Calculate frequency of each skill
skill_counts <- tibble(skill = all_skills) %>%
  count(skill, sort = TRUE)

# Combine the "skills" columns from both datasets
combined_skills <- c(dat_dice$skills, dat_2$skills)

# Split the combined skills vector by commas to get individual skills
individual_skills <- combined_skills %>%
  strsplit(",\\s*") %>%
  unlist()

# Calculate frequency of each skill
skill_counts_combined <- tibble(skill = individual_skills) %>%
  count(skill, sort = TRUE)

colnames(skill_counts_combined)[2] <- "Frequency"
```

```{r clean_data courses}

# Filter only for English courses
dat <- dat[language == "English",]

# Convert published date
dat <- dat[, published_date := as.Date(published_time)]

# Convert the column to date format
dat <- dat[, last_update_date := as.IDate(last_update_date, format = "%d/%m/%Y")]
dat[last_update_date == "", last_update_date := NA]

# Replace blanks with NULL in the "topic" column
dat <- dat[topic == "", topic := NA]

# Calculate duration per lecture
dat <- dat[, duration_per_lecture := round(content_length_min / num_lectures, 2)]
dat <- dat[is.na(duration_per_lecture), duration_per_lecture := 0]

```


```{r prep reviews data}
# only keep english courses
udemy.eng <- dat[language == "English",]

# only keep english comments
language_detection <- cld2::detect_language(udemy.comments$comment)
udemy.comments.eng <- udemy.comments[, lang := language_detection][lang == "en", ]

# make course id numeric type
udemy.comments.eng$course_id <- as.numeric(udemy.comments.eng$course_id)

# merge course & reviews
udemy.merged <- merge(udemy.comments.eng, udemy.eng, by.x ='course_id', by.y= 'id', multiple = "all")

#date time as only date
udemy.merged$date <- as.Date(udemy.merged$date)
reviews <- udemy.merged[, .(review.id = id, course = title, date = date, 
                                         rating = rate, subscribers = num_subscribers, price = price, category = category, 
                                          topic = topic, subcategory = subcategory, instructor = instructor_name, review = comment)]

# Due to the large amount reviews, we will subset reviews for the most recent 3 years
reviews.2020 <- reviews[date >= '2020-01-01' & date < '2021-01-01',]
reviews.2021 <- reviews[date >= '2021-01-01' & date < '2022-01-01',]
reviews.2022 <- reviews[date >= '2022-01-01' & date < '2023-01-01',]
```


```{r functions}
# this function calls above subset of reviews
year.cat <- function(year, cat){
  if(year == "2022"){
    rev <- reviews.2022
  }
  if(year == "2021"){
    rev <- reviews.2021
  }
  if(year == "2020"){
    rev <- reviews.2020
  }
  rev.cat <- rev[category == cat, .(review.id = review.id, review = review)]
  return(rev.cat)
}

```

```{r define_variables}

dat[, "rating_group" := cut(
  avg_rating,
  breaks = c(-Inf, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, Inf),
  labels = c("Not rated", "<=0.5", ">0.5 - 1.0", ">1.0 - 1.5", ">1.5 - 2.0", ">2.0 - 2.5", ">2.5 - 3.0", ">3.0 - 3.5", ">3.5 - 4.0", ">4.0 - 4.5", ">4.5 - 5.0"), 
  right = TRUE
)]

dat[, "duration_group" := cut(
  content_length_min,
  breaks = c(-Inf, 0, 3000, 6000, 9000, 12000, 15000, 18000, 21000, Inf),
  labels = c("Free", ">0 - 3000", ">3000 - 6000", ">6000 - 9000", ">9000 - 12000", ">12000 - 15000", ">15000 - 18000", ">18000 - 21000", ">21000"),  
  right = TRUE
)]

dat[, "duration_lect_group" := cut(
  duration_per_lecture,
  breaks = c(-Inf, 0, 30, 60, 90, 120, 150, 180, 210, Inf),
  labels = c("Free", ">0 - 30", ">30 - 60", ">60 - 90", ">90 - 120", ">120 - 150", ">150 - 180", ">180 - 210", ">210"),  
  right = TRUE
)]

dat[, "price_group" := cut(
  price,
  breaks = c(-Inf, 0, 100, 200, 300, 400, 500, 600, 700, 800, 900, Inf),
  labels = c("Free", ">0 - 100", ">100 - 200", ">200 - 300", ">300 - 400", ">400 - 500", ">500 - 600", ">600 - 700", ">700 - 800", ">800 - 900", ">900"),  
  right = TRUE
)]

unique.paid <- dat[, sort(unique(get(paid.name)))]
unique.categories <- dat[, sort(unique(get(category.name)))]
unique.subcategories <- dat[, sort(unique(get(subcategory.name)))]
unique.topics <- dat[, sort(unique(get(topic.name)))]

unique.rating.groups <- dat[, sort(unique(get(rating.group.name)))]
unique.duration.groups <- dat[, sort(unique(get(duration.group.name)))]
unique.duration.lect.groups <- dat[, sort(unique(get(duration.lect.group.name)))]
unique.price.groups <- dat[, sort(unique(get(price.group.name)))]

```


Introduction
=====================================  

Here is a dashboard on the skills in demand by employers, courses offered by key competitor Udemy and sentiment analyses of learners.

There are `r dat[, .N]` courses, `r dat[, length(unique(get(category.name)))]` unique categories, `r dat[, length(unique(get(topic.name)))]` unique skills, `r dat[, length(unique(get(instructor.name)))]` instructors, and `r reviews[, length(unique(review.id))]` reviews.

Click on the tabs to see different reports.


1.Skills in Demand
===================================

What are the top skills employers are looking for

Row {data-height=500}
-------------------------------------

```{r 1_input}
inputPanel(
  sliderInput(inputId = "Skills_Chart_Skills", label = "Show Top Skills", min = 1, max = 30, value = 10, step = 1)
)

```

```{r 1_output}

renderPlot({
  top_skills_data <- head(skill_counts_combined, input$Skills_Chart_Skills)  # Select the top skills based on user input
  top_skills_data <- top_skills_data %>% arrange(desc(Frequency))  # Sort the data in descending order of frequency
  
  # Create the bar chart
  ggplot(top_skills_data, aes(x = reorder(skill, -Frequency), y = Frequency)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    labs(title = "Top Skills Overall",
         x = "Skill",
         y = "Number of Times Appears") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})

```


2. Skills Offered
=====================================  

What are the top 10 skills learnt among the paid or free courses with the rating range in the selected category?

Row {data-height=500}
-------------------------------------

```{r 4_input}

inputPanel(
  selectInput(inputId="rating_paid_variable", label = "Is Paid", choices = unique.paid, selected = unique.paid, multiple = TRUE),
  selectInput(inputId="rating_category_variable", label = "Category", choices = unique.categories, selected = unique.categories, multiple = TRUE),
  sliderInput(inputId = "rating_min", label = "Min rating", min = 0, max = 4.5, value = 4, step = 0.5),
  sliderInput(inputId = "rating_max", label = "Max rating", min = 0.5, max = 5, value = 5, step = 0.5)
)

# input = list(rating_paid_variable = all, rating_category_variable = all, rating_min = 4, rating_max = 5)

```

```{r 4_output}

renderDataTable({
  top <- dat[get(paid.name) %in% input$subscription_paid_variable & get(rating.name) >= input$rating_min & get(rating.name) <= input$rating_max & get(category.name) == input$rating_category_variable,  ] 
  tab <- percentage.table(x = top[, get(topic.name)])
  tab <- data.table(tab)
  setnames(tab, c("x", "N"), c("Skill", "Percentage"))
  datatable(tab[order(-Percentage)][1:10, ],
            options = list(scrollY = "300px"))
})

```


3. Subscription
=====================================  

What are the top subscribed courses for selected category?

Row {data-height=500}
-------------------------------------

```{r 3_input}

inputPanel(
     selectInput(inputId="subscription_paid_variable", label = "Is Paid", choices = unique.paid, selected = unique.paid, multiple = TRUE),
  selectInput(inputId="subscription_category_variable", label = "Select Category:", choices = unique.categories, selected = unique.categories[1]),
    sliderInput(inputId = "subscription_rating_min", label = "Min rating", min = 0, max = 4.5, value = 4, step = 0.5),
  sliderInput(inputId = "subscription_rating_max", label = "Max rating", min = 0.5, max = 5, value = 5, step = 0.5),
  sliderInput(inputId = "courses_number", label = "Show Top Courses", min = 1, max = 20, value = 5, step = 1)
)

# input <- list(subscription_paid_variable = ALL, subscription_category_variable = category.variables[1], subscription_rating_min = 4, subscription_rating_max = 5, courses_number = 5)

```

```{r 3_output}

renderDataTable({
  filtered_data <- dat[get(paid.name) %in% input$subscription_paid_variable & get(category.name) == input$subscription_category_variable & get(rating.name) >= input$subscription_rating_min & get(rating.name) <= input$subscription_rating_max, ]
  top_subscribed_courses <- filtered_data[order(-num_subscribers), .(title, num_subscribers)][1:input$courses_number]
  datatable(top_subscribed_courses,
            options = list(scrollY = "200px"))
  })


```


4. Cross-Tab
=====================================  

What is the distribution of courses by duration and price for the indicated skill?

```{r 8_input}

inputPanel(
  textInput(inputId = "skills", label = "Indicate Skill:", value = "Python", width = "200px", placeholder = "Enter skill here")
)

# input = list(skills = "Python")

```

Row {data-height=500}
-------------------------------------

```{r 8_output}

renderDataTable({
  filtered_data <- dat[grepl(input$skills, dat$topic, ignore.case = TRUE) | 
                     grepl(input$skills, dat$category, ignore.case = TRUE) | 
                     grepl(input$skills, dat$subcategory, ignore.case = TRUE), ]
    results <- xtabs(~get(price.group.name) + get(duration.group.name), data = filtered_data)
    results_df <- as.data.frame.matrix(results)
    datatable(results_df, options = list(scrollY = "300px"))
})

```



5. Duration (Course)
=====================================  

What is the distribution of paid or free courses by duration for the selected category? 

Row {data-height=500}
-------------------------------------

```{r 5_input}

inputPanel(
  selectInput(inputId="duration_paid_variable", label = "Is Paid", choices = unique.paid, selected = unique.paid, multiple = TRUE),
  selectInput(inputId="duration_category_variable", label = "Category", choices = unique.categories, selected = unique.categories, multiple = TRUE),
  sliderInput(inputId = "duration_min", label = "Min duration (Mins)", min = 1, max = 21600, value = 1, step = 720),
  sliderInput(inputId = "duration_max", label = "Max duration (Mins)", min = 720, max = 22570, value = 720, step = 720)
)

# input = list(duration_paid_variable = all, duration_category_variable = all, duration_min = 1, duration_max = 720)

```

```{r 5_output}

renderPlot({
  
  # Set the desired range, number of bins, and interval
  min_val <- input$duration_min
  max_val <- input$duration_max
  num_bins <- 12
  interval <- (max_val - min_val) / num_bins
  
  # Filter the data within the specified range
  filtered_data <- dat[get(paid.name) %in% input$duration_paid_variable & get(duration.name) >= min_val & get(duration.name) <= max_val & get(category.name) %in% input$duration_category_variable, ]

  # Create the histogram
  hist_data <- hist(filtered_data$content_length_min, breaks = seq(min_val, max_val, by = interval), plot = FALSE)
  
  # Plot the histogram bars with count values
  plot(hist_data, col = "lightblue", border = "white", xlab = "Duration (in minutes)", ylab = "Count", main = "Histogram of Duration", xaxt = "n")
  text(hist_data$mids, hist_data$counts, labels = hist_data$counts, col = "black", cex = 0.6, pos = 1)
  
  # Define the x-axis labels with horizontal orientation
  axis(1, at = seq(0, max_val, by = 60), las = 1)

})

```

6. Duration (Lecture)
=====================================  

What is the distribution of paid or free courses by duration per lecture for the selected category?

Row {data-height=500}
-------------------------------------

```{r 6_input}

inputPanel(
  selectInput(inputId="duration_lect_paid_variable", label = "Is Paid", choices = unique.paid, selected = unique.paid, multiple = TRUE),
  selectInput(inputId="duration_lect_category_variable", label = "Category", choices = unique.categories, selected = unique.categories, multiple = TRUE),
  sliderInput(inputId = "duration_lect_min", label = "Min duration (Mins)", min = 0.01, max = 230, value = 0.01, step = 5),
  sliderInput(inputId = "duration_lect_max", label = "Max duration (Mins)", min = 1, max = 240, value = 30, step = 5)
)

# input = list(duration_lect_paid_variable = all, duration_lect_category_variable = all, duration_lect_min = 1, duration_lect_max = 720)

```

```{r 6_output}

renderPlot({
  
  # Set the desired range, number of bins, and interval
  min_val <- input$duration_lect_min
  max_val <- input$duration_lect_max
  num_bins <- 10
  interval <- (max_val - min_val) / num_bins
  
  # Filter the data within the specified range
  filtered_data <- dat[get(paid.name) %in% input$duration_lect_paid_variable & get(duration.lect.name) >= min_val & get(duration.lect.name) <= max_val & get(category.name) %in% input$duration_lect_category_variable, ]

  # Create the histogram
  hist_data <- hist(filtered_data$duration_per_lecture, breaks = seq(min_val, max_val, by = interval), plot = FALSE)
  
  # Plot the histogram bars with count values
  plot(hist_data, col = "lightblue", border = "white", xlab = "Duration (in minutes)", ylab = "Count", main = "Histogram of Duration per Lecture", xaxt = "n")
  text(hist_data$mids, hist_data$counts, labels = hist_data$counts, col = "black", cex = 0.6, pos = 1)
  
  # Define the x-axis labels with horizontal orientation
  axis(1, at = seq(0, max_val, by = 3), las = 1)
  
})

```

7. Prices
=====================================  

What is the distribution of courses by prices for the selected category? 

Row {data-height=500}
-------------------------------------

```{r 7_input}

inputPanel(
  selectInput(inputId="price_category_variable", label = "Category", choices = unique.categories, selected = unique.categories, multiple = TRUE),
  sliderInput(inputId = "price_min", label = "Min price", min = 0, max = 990, value = 0, step = 100),
  sliderInput(inputId = "price_max", label = "Max price", min = 100, max = 1000, value = 100, step = 100)
)

# input = list(price_category_variable = all, price_min = 0, price_max = 10)

```

```{r 7_output}

renderPlot({
  
  dat_paid <- dat[is_paid == TRUE, ]
  
  # Set the desired range, number of bins, and interval
  min_val <- input$price_min
  max_val <- input$price_max
  num_bins <- 10
  interval <- (max_val - min_val) / num_bins
  
  # Filter the data within the specified range
  filtered_data <- dat_paid[get(price.name) >= min_val & get(price.name) <= max_val & get(category.name) %in% input$price_category_variable, ]
  
  # Create the histogram
  hist_data <- hist(filtered_data$price, breaks = seq(min_val, max_val, by = interval), plot = FALSE)
  
  # Plot the histogram bars with count values
  plot(hist_data, col = "lightblue", border = "white", xlab = "Price", ylab = "Count", main = "Histogram of Price")
  text(hist_data$mids, hist_data$counts, labels = hist_data$counts, col = "black", cex = 0.6, pos = 1)

})

```

8. Models
=====================================  

Row {data-height=500}
-------------------------------------

```{r 9_input}

inputPanel(
 
  selectInput(inputId= "reg_outcome_var", label = "Outcome Variable:", choices = outcome.var, selected = outcome.var[1]),
  
    selectInput(inputId = "reg_inputs", label = "Choose Inputs:", choices = c(lectures.name, reviews.name, comments.name, duration.name, category.name, price.name, subscribers.name, rating.name), selected = c(lectures.name, reviews.name, comments.name, duration.name, category.name, price.name, subscribers.name, rating.name), multiple = TRUE)
)

# input = list(reg_outcome_var = outcome.var[1], reg_inputs = ALL)

```

Row {data-height=500}
-------------------------------------

```{r 9_output}

renderDataTable({

  res <- fit.model(dt = dat, outcome.name = input$reg_outcome_var, input.names = input$reg_inputs, model.type = "linear")
  
  datatable(data = res, options = list(scrollY = "300px"))
  
})


```

9. Review Sentiments
=====================================  

What are the most frequently appearing words in the **positive / negative** reviews of each course category in a selected year?    
( Please note that due to the huge amount of data processing, word cloud can take up to 30 seconds to generate. )  
  

Row {data-height=500}
-------------------------------------

```{r q1_input}
inputPanel(
  selectInput(inputId="year", label = "Select Year:", choices = years, selected = years[1]),
  selectInput(inputId="pos.neg", label = "Select Reviews:", choices = pos.neg, selected = pos.neg[2]),
  selectInput(inputId="category", label = "Select Category:", choices = unique.categories, selected = unique.categories[6]),
  #checkboxInput(inputId = "wordcloud", label = "Show Word Cloud", value = FALSE)
)
```

Row {data-height=500}
-------------------------------------

```{r q1_output}
renderWordcloud2({
  year.skill <- year.cat(input$year, input$category) 
  #score
  score <- afinn.score(year.skill)

  #positive word frequency
  if(input$pos.neg == "Positive"){
    word_freq_count <- word.freq(score, year.skill, TRUE)
  }
  if(input$pos.neg == "Negative"){
    word_freq_count <- word.freq(score, year.skill, FALSE)
  }
  colorVec = rep(c('mediumpurple', 'lightskyblue'), length.out=nrow(word_freq_count))
  wordcloud2(word_freq_count, size = 0.5, fontFamily= 'arial', color = colorVec)
})
```

